\systemEnding: Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
tiny edit in abstract

\begin{abstract}
  Successful approaches to program induction require a hand-engineered
  domain-specific language (DSL), constraining the space of allowed
  programs and imparting prior knowledge of the domain.  We contribute
  a program induction algorithm called \system that learns a DSL and
  trains a neural network to efficiently search for programs in the
  learned DSL.  We use our model to build circuits, edit strings, do
  symbolic regression, and synthesize functions on lists, in each case
  showing the model learns a domain-specific vocabulary for expressing
  solutions to the problems in the domain.

>>>>

\begin{abstract}
  Successful approaches to program induction require a hand-engineered
  domain-specific language (DSL), constraining the space of allowed
  programs and imparting prior knowledge of the domain.  We contribute
  a program induction algorithm called \system that learns a DSL and
  trains a neural network to efficiently search for programs in the
  learned DSL.  We use our model to build circuits, edit strings, do
  symbolic regression, and synthesize functions on lists, in each case
  showing the model learns a domain-specific vocabulary for expressing
  solutions to problems in the domain.
